Title
========================================================


Firstly, load or install required packages...
```{r, prepare_environment,cache=FALSE}
source("functions.R")
load_libraries()

```

Now, get the data from the file in the variable: `raw_filename`.

```{r, load_data, cache=FALSE}
#these data are FPKM from DOI: 10.1371/journal.pone.0074183
raw_filename = "~/Desktop/gene_nets/fpkm_data.csv"
data <- read.csv(raw_filename, header=TRUE)
```

Subset the FPKM into one `data.frame` for each treatment.

```{r, subset_data,cache=FALSE}
#change 0s to NA
data[data == 0] <- NA

#subset
mock <- data[c("tracking_id", "MOCK_1_1","MOCK_1_2","MOCK_6_1","MOCK_6_2","MOCK_12_1","MOCK_12_2")]
avr <- data[c("tracking_id","AVR_1_1","AVR_1_2","AVR_6_1","AVR_6_2","AVR_12_1","AVR_12_2")]
vir <- data[c("tracking_id","VIR_1_1","VIR_1_2","VIR_6_1","VIR_6_2","VIR_12_1","VIR_12_2")]
```

Filter out genes that do not show `X` Fold or better change relative to the 1h timepoint and do not have complete data at each timepoint.
```{r, filter_data,cache=FALSE}
x <- 10
mock <- get_diff_expressed(mock, x, "MOCK")
avr <- get_diff_expressed(avr, x,  "AVR")
vir <- get_diff_expressed(vir, x, "VIR")

#make lists of gene names
mock_nodelabels <- get_nodelabels(mock)
avr_nodelabels <- get_nodelabels(avr)
vir_nodelabels <- get_nodelabels(vir)

```

Get some Affy array data in for FLG-22 treatments too

```{r}
flg22 <- read.table("~/Desktop/gene_nets/just_data_sig_in_both_time_points.txt")
flg22 <- as.matrix(flg22)
flg22 <- t(flg22)

flg22_nodelabels <- as.character(read.table("~/Desktop/gene_nets/node_labels_sig_in_both_times.txt")$V1)
```

How many genes are we using for each data set?

```{r, summary_counts}
data.frame(mock=length(mock_nodelabels),avr=length(avr_nodelabels),vir=length(vir_nodelabels),flg22=length(flg22_nodelabels))
```

Make the data structure for the PCC and GGM
```{r, make_long,cache=FALSE}
mock_long <- make_longitudinal(mock)
avr_long <- make_longitudinal(avr)
vir_long <- make_longitudinal(vir)
flg22_long <- as.longitudinal(flg22, repeats=c(3,3), time=c(2,4))
### check all went well...
is.longitudinal(mock_long)
```

Generate the PCC and find `y` edges with a GGM
```{r,find_interactions,cache=FALSE}
y <- 250
mock_edges <- make_net(mock_long,y)
avr_edges <- make_net(avr_long,y)
vir_edges <- make_net(vir_long,y)
flg22_edges <- make_net(flg22_long,y)

mock_igr <- network.make.igraph(mock_edges, mock_nodelabels)
avr_igr<- network.make.igraph(avr_edges, avr_nodelabels)
vir_igr<- network.make.igraph(vir_edges, vir_nodelabels)

flg22_igr <- network.make.igraph(flg22_edges, flg22_nodelabels)

union <- graph.union(mock_igr,avr_igr,vir_igr, flg22_igr)
```

```{r}
plot(mock_igr,layout=layout.spring,
 edge.arrow.size=0.5, vertex.size=9, vertex.label.cex=0.7, edge.color='red')

```

```{r}
plot(avr_igr,layout=layout.auto,
 edge.arrow.size=0.5, vertex.size=9, vertex.label.cex=0.7, edge.color='blue')

```

```{r}
plot(union,layout=layout.auto,
 edge.arrow.size=0.5, vertex.size=14, vertex.label.cex=1.2, edge.color='green')

```

```{r,cache=FALSE,message=FALSE, warning=FALSE, results='hide'}
library('HiveR')
mock_hive <- make_annotated_hive(mock_igr)
avr_hive <- make_annotated_hive(avr_igr)
vir_hive <- make_annotated_hive(vir_igr)
flg22_hive <- make_annotated_hive(flg22_igr)

```

```{r}
library(plyr)

 
# Change the node color and size based on node degree and betweenness values
plotHive(mock_hive, method = "abs", bkgnd = "black",   axLabs = c("source", "hub", "sink"), axLab.pos = 1)
plotHive(avr_hive, method = "abs", bkgnd = "black",   axLabs = c("source", "hub", "sink"), axLab.pos = 1)
plotHive(vir_hive, method = "abs", bkgnd = "black",   axLabs = c("source", "hub", "sink"), axLab.pos = 1)
plotHive(flg22_hive, method = "abs", bkgnd = "black",   axLabs = c("source", "hub", "sink"), axLab.pos = 1)
```

```{r}
library(venneuler)
library(stringr)
mock_genes <- str_sub(V(mock_igr)$name, 1,9 )
avr_genes <- str_sub(V(avr_igr)$name, 1, 9)
vir_genes <- str_sub(V(vir_igr)$name, 1, 9)
flg22_genes <- V(flg22_igr)$name


euler <- make_fourway_euler_diagram(mock_genes, avr_genes, vir_genes, flg22_genes)
plot(euler)
```

```{r}
  rand_mock <- sample(mock_nodelabels,length(mock_genes))
  rand_avr <- sample( avr_nodelabels, length(avr_genes))
  rand_vir <- sample( vir_nodelabels,length(vir_genes))
  rand_flg22 <- sample(flg22_nodelabels, length(flg22_genes))
  rand_euler <- make_fourway_euler_diagram(rand_mock, rand_avr, rand_vir, rand_flg22)
  plot(rand_euler)
```

```{r}
  write.table(get.edgelist(mock_igr),"mock_edges.txt",col.names=FALSE, row.names=FALSE)
  write.table(get.edgelist(avr_igr),"avr_edges.txt",col.names=FALSE, row.names=FALSE)
  write.table(get.edgelist(vir_igr),"vir_edges.txt",col.names=FALSE, row.names=FALSE)
  write.table(get.edgelist(flg22_igr),"flg22_edges.txt",col.names=FALSE, row.names=FALSE)
  
```